---
title: "Stroke Prediction"
author: "Michal Rackieqicz"
format: gfm
editor: visual
---

# About Data Analysis Report

This RMarkdown file contains the report of the data analysis done for the project on building and deploying a stroke prediction model in R. It contains analysis such as data exploration, summary statistics and building the prediction models. The final report was completed on `r date()`. 

**Data Description:**

According to the World Health Organization (WHO) stroke is the 2nd leading cause of death globally, responsible for approximately 11% of total deaths.

This data set is used to predict whether a patient is likely to get stroke based on the input parameters like gender, age, various diseases, and smoking status. Each row in the data provides relevant information about the patient.


# Data preprocessing

## Load data and packages

```{r packages}
#| message: false
library(GGally)
library(ggExtra)
library(skimr)
library(tidymodels)
library(tidyverse)
```

```{r data}
#| message: false
stroke <- readr::read_csv("data-raw/healthcare-dataset-stroke-data.csv")
```

## EDA

```{r}
skim(stroke)
```

```{r}

```

### Findings and Summary

# Build prediction models

```{r}

```




# Model evaluation and selection

```{r}

```



# Model deployment

```{r}

```




# Findings and Conclusions
